---
title: "paired_ratio_data"
author: "Akoua Orsot"
date: "2023-10-19"
output: html_document
---

# INVESTIGATION

1.  Check for a similar Simpson's paradox situations in all of the paired t-testing.

2.  Plot histograms for the pre-connection income, post-connection income, and paired differences.

3.  Ask Ken and Sam to help us identify what is going on with the negative-paired-difference people. Let's do this together. I have a theory that, before electrification, some community members make themselves wealthy by providing services to people that they can get more cheaply after electrification. For example, before we built the Kalobeyei Settlement mini-grid, a few dozen community members paid one guy with a diesel generator for electricity using little more than an extension cord between the genset and their homes.

# Importing Libraries

```{r}
# Importing libraries
library(data.table)
library(ggplot2)
library(dplyr)
library(lessR)
library(tidyr)
library(ggpubr)
library(tibble)
library(psych)
library(stringr)
library(writexl)
library(data.table)
```

# Data

```{r cars}
## Locading the cleaned data sets
initial_cols <- c("renewvia_id","status", 
                "country", "gender", "community",
                "avg_household_income", "appliances_count", 
                "cellphones_count", "light_hours_current",
                "kerosene_lamps_count")
post_cols <- c("renewvia_id",
          "country", "gender", "community",
                "avg_household_income", "appliances_count", 
                "cellphones_count", "light_hours_current",
                "kerosene_lamps_count")

# Intial Survey
initial_path <- "data_cleaning/datasets_clean/initial_clean.csv"
initial_clean <- read.csv(initial_path)[, initial_cols]
initial_clean$light_hours_current <- replace(initial_clean$light_hours_current,
  initial_clean$light_hours_current > 24, NA)

# Pre-connection
initial_pre <- (initial_clean %>% 
                  filter(status == "pre_connection"))
# Post-connection
initial_post <- (initial_clean %>% 
                   filter(status == "post_connection"))

# Household Post-Survey
post_path <- "data_cleaning/datasets_clean/post_clean.csv"
post_clean <- read.csv(post_path)[, post_cols]

## Pairing pre and post responses
paired_clean <- merge(initial_pre, post_clean,
                      suffix = c("_pre", "_post"),
                      by= 'renewvia_id')

# head(initial_pre)
# head(post_clean)
# head(paired_clean)
```

# Descriptive Stats

```{r}
# Function
get_stats <- function(data, ct, var_name,data_source, 
                      remove_outliers = FALSE, 
                      exclude_zeros = FALSE) {
  if (grepl("_pre", var_name, fixed = TRUE)){
    country_data <- data %>% filter(country_pre == ct)
  } else if (grepl("_post", var_name, fixed = TRUE)){
    country_data <- data %>% filter(country_post == ct)
  } else {country_data <- data %>% filter(country == ct)}
    
  if (remove_outliers == TRUE) {
    print("Excluding outliers")
    quartiles <- quantile(country_data[, var_name], 
                        probs=c(.25, .75), na.rm = TRUE)
  
    IQR <- IQR(country_data[, var_name], na.rm = TRUE)
    
    Lower <- quartiles[1] - 1.5*IQR
    Upper <- quartiles[2] + 1.5*IQR 
    
    country_data <- subset(country_data, 
                              country_data[, var_name] > Lower &
                              country_data[, var_name] < Upper)
  } 
  
  var <- country_data[, var_name]
  
  if (exclude_zeros == TRUE) {
    print("Removing Zeros")
    var <- var[var != 0]
  } 
  
  stats <- t(describe(var, IQR=TRUE, quant=c(.1,.25,.5,.75,.90),))
  print(t.test(var, conf.level = 0.95))
  hist_title <- paste(filt_ct, data_source, " : ", var_name)
  print(stats)
  return(hist(var, main=hist_title))
}


# Running the paired t-test
paire_t_test <- function(df, ct, title, var_name) {
  df_country <- df %>% filter(country_pre == ct)
  pre_name <- paste(var_name, "post", sep="_")
  post_name <- paste(var_name, "pre", sep="_")
  df_country$diff <- as.numeric(df_country[, post_name] - df_country[, pre_name])
  # df_new <- df_country %>% filter(diff > -20)
  var_pre <- df_country[, paste(var_name, "pre", sep="_")]
  var_post <- df_country[, paste(var_name, "post", sep="_")]
 # diff <- var_post - var_pre
  
  hist_title <- paste(ct, " - ", 
                      title, "Difference")
  print(var_name)
  print(t.test(var_pre, var_post,
         paired = TRUE, alternative = "two.sided"),
        detailed = TRUE)
  return(hist(df_country$diff, main = hist_title))
}
```

```{r}
filt_ct <- "nigeria"
col_name <- "avg_household_income"
paire_t_test(paired_clean, filt_ct, col_name, title="Light Hours")
col_name_pre <- paste(col_name, "pre", sep="_")
col_name_post <- paste(col_name, "post", sep="_")
# Initial Pre-Connection
get_stats(initial_pre, filt_ct, col_name, data_source="intial_pre",
          exclude_zeros = TRUE)
# Post-Connection Survey
get_stats(post_clean, filt_ct, col_name,data_source="post",
          exclude_zeros = TRUE)
## Paired Data
# Pre-Connection
get_stats(paired_clean, filt_ct, col_name_pre, data_source="paired",
          exclude_zeros = TRUE)
# Post-Connection
get_stats(paired_clean, filt_ct, col_name_post, data_source="paired",
          exclude_zeros = TRUE)
```

```{r}
filt_ct <- "kenya"

countries <- c("nigeria", "kenya")
col_name <- "avg_household_income"
num_vars <- c("avg_household_income", "appliances_count", 
                "cellphones_count", "light_hours_current",
                "kerosene_lamps_count")
dfs <- c(initial_pre, post_clean, paired_clean)
dfs_names <- c("intial_pre", "post")
var_names <- c(col_name, 
              paste(col_name, "pre", sep="_"), 
              paste(col_name, "post", sep="_"))

paire_t_test(paired_clean, filt_ct, col_name, title="Light Hours")

# Initial Pre-Connection
get_stats(initial_pre, filt_ct, col_name, data_source="intial_pre",
          exclude_zeros = TRUE)
# Post-Connection Survey
get_stats(post_clean, filt_ct, col_name,data_source="post",
          exclude_zeros = TRUE)
## Paired Data
# Pre-Connection
get_stats(paired_clean, filt_ct, col_name_pre, data_source="paired",
          exclude_zeros = TRUE)
# Post-Connection
get_stats(paired_clean, filt_ct, col_name_post, data_source="paired",
          exclude_zeros = TRUE)
```

# Hypothesis Testing

```{r}



# neg_diff <- (paired_clean %>% filter(diff < 0))[, c("renewvia_id", 
#                                                    "country_pre",
#                                                  "light_hours_current_pre",
#                                                  "light_hours_current_post",
#                                                  "diff")
#              ]

```

```{r}
col_names <- c("avg_household_income", "appliances_count", 
                "cellphones_count", "light_hours_current",
                "kerosene_lamps_count")
diff_cols <- c("renewvia_id")
for (col_name in col_names) {
  new_col <- paste("diff", col_name, sep="_")
  diff_cols <- c(diff_cols, new_col)
  pre_name <- paste(col_name, "pre", sep="_")
  post_name <- paste(col_name, "post", sep="_")
  paired_clean[, new_col] <- as.numeric(paired_clean[, post_name] - 
                                   paired_clean[, pre_name])
  # sprintf("%s: Sum of difference = %.2f, Mean of difference = %.2f", 
  #       col_name, sum(paired_clean[, new_col],na.rm = TRUE), 
  #       mean(paired_clean[, new_col],na.rm = TRUE))
}
```

```{r}
diffs <- paired_clean[, diff_cols]
# diffs[, sapply(diffs, FUN = function(x) !any(x < 0))]
diffs[which(apply(diffs, 1, function(row) any(row < 0))),]
```

```{r}
tariffs <- read.csv("data_cleaning/customers_tariffs.csv")
neg_diff_customers <- merge(neg_diff, tariffs,
                            by.x='renewvia_id',
                            by.y="customerAccountNumber",
                            all.x=TRUE)
kenya_neg_diff <- neg_diff_customers %>% filter(country_pre == "kenya")
nigeria_neg_diff <- neg_diff_customers %>% filter(country_pre == "nigeria")
write_xlsx(kenya_neg_diff,"kenya_customers_income_diff.xlsx")
write_xlsx(nigeria_neg_diff,"nigeria_customers_income_diff.xlsx")
```

```{r}
post_clean[duplicated(post_clean$renewvia_id), ]
```
